Flatiron cleaning

### 2021-10-13 Rmd/rdi analysis.Rmd
Add model, fix typo/text, add cleaning

```{r}
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(chemotherapy_type, therapy, treatment_sequence) %>% 
  tbl_summary(by = therapy)
```

@@

`r emo::ji("question_mark")`  
Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
Should we include patients who got a single drug as lot/line? like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others? `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>

```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
remove_linename_other <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
  select(patientid, linename, linenumber, linenumber_new, linenumber_adj, drug_count, 
         drugname, chemotherapy_type, therapy, treatment_sequence, episodedate) %>%

@@

Some patients had part of their first line switched to Adjuvant line. How long is this adjuvant line?
```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate, end = lineenddate)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, linenumber, linenumber_new, linenumber_adj, 
         drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= line_duration))+
  geom_bar(color = "slateblue") +
  theme_minimal()+
  ggforce::facet_zoom(xlim = c(0, 200), zoom.size = 1)
```

@@

# therapy_line %>% 
#   mutate(change_line = case_when(
#     linenumber == 1 & 
#       linenumber_new == 2 &
#       chemotherapy_type == "Adjuvant" &
#       treatment_sequence == "neo + surg + adj"     ~ 1,
#     TRUE                                           ~ 0
#   )) %>% 
#   filter(change_line == 1) %>% 
#   group_by(patientid) %>% 
#   mutate(firstdate = first(episodedate)) %>% 
#   mutate(lastdate = last(episodedate)) %>% 
#   ungroup() %>% 
#   mutate(time_of_switch_line = interval(start = firstdate, end = lastdate) / duration(n =1, units = "days")) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x=time_of_switch_line, fill = ..count..))+
#   geom_histogram(binwidth = 7)+
#   theme_minimal()+
#   ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
#   scale_y_continuous(#breaks=c(0, 50, 100, 150),
#                      minor_breaks=c(10, 20, 30, 40)#,
#                      #labels = c(0, 50, 100, 150)
#   )
```
<!-- `r emo::ji("question_mark")`   -->
<!-- <span style="color:red">**So the bigger question is : Is it acceptable to include the patients who have a switched line?**</span> -->

@@

```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_creat = case_when(
    interval_creat < 31 &
      creat_date > linestartdate &
      creat_date < lineenddate             ~ interval_creat,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with weight
  left_join(. , weight, by = "patientid") %>%
  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
                        duration(n=1, unit="days"))) %>%
  mutate(interval_weight = case_when(
    interval_weight < 31 &
      weight_date > linestartdate &
      weight_date < lineenddate             ~ interval_weight,
    TRUE                                    ~ NA_real_
  )) %>% 
  arrange(interval_weight) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
         cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with body_surface_area
  left_join(., body_surface_area, by = "patientid") %>%
  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
                          duration(n=1, unit="days"))) %>%
  mutate(interval_bsa = case_when(
    interval_bsa < 31 &
      bsa_date > linestartdate &
      bsa_date < lineenddate               ~ interval_bsa,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_bsa) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
  select(-bsa_du_bois) %>%

  # Merge with auc
  left_join(., areaUC, by = c("patientid", "drugname")) %>%
  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_auc = case_when(
    interval_auc < 31 &
      auc_date > linestartdate &
      auc_date < lineenddate               ~ interval_auc,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_auc) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

# A little of data analysis
## Explore the dataset

@@

Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
<br>

@@

<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
```{r Table 1}
analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, 
           agecat, "ageatdx",

@@

```{r Table 3}
# tbl1 <- 
  analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "debulking",
           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

@@

  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("highly underdose", "underdose", "correct", "perfect", "higher dose", "overdose")))
```

```{r}
Frontline %>% distinct(patientid) %>% nrow()
```

@@

## 2.Plots Clinical
<div class = "row">
<div class = "col-md-6">
```{r plot clinical}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= histology))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Histology")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= stagecat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Stage")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= agecat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Age cat")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_germline))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BRCA gernline")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_tumor))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BRCA tumor")+
  coord_flip()
```
</div>

<div class = "col-md-6">
```{r}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = bmi_cat))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = histology))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Histology")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = stagecat))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Stage")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = agecat))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Age cat")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = brca_germline))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BRCA germline")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = brca_tumor))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BRCA tumor")+
  coord_flip()
```
</div>
</div>

@@

```{r treatment table}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           had_neo, had_adj,
           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p(
    # test.args = all_tests("chisq.test") ~ list(workspace=2e9)
    ) %>% bold_p(t = .05)
# tbl2 <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

## 2.Plots Treatment
<div class = "row">
<div class = "col-md-6">
```{r treatment plots}
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

# Frontline %>% 
#   arrange(episodedate) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   group_by(chemotherapy_type) %>% 
#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
#   geom_bar(stat="identity")+
#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
#   theme_minimal()+
#   guides(fill = FALSE) +
#   coord_flip()

>>>>

```{r}
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(had_neo, had_adj, therapy) %>% 
  tbl_summary(by = therapy,
              type = list(had_neo ~ "dichotomous", 
                          had_adj ~ "dichotomous"),
              missing = "no")
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(therapy, treatment_sequence) %>% 
  tbl_summary(by = therapy)
```

@@

`r emo::ji("question_mark")`  
Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
Should we include patients who got a single drug as lot/line? like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others? `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>    
`r emo::ji("check")`   
```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
remove_linename_other <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
  select(patientid, linename, linenumber, linenumber_new, linenumber_adj, drug_count, 
         drugname, chemotherapy_type, therapy, treatment_sequence, episodedate) %>%

@@

Patients with part of their first line switched to Adjuvant line because of surgery. How long is this adjuvant line?
```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate, end = lineenddate)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, linenumber, linenumber_new, linenumber_adj, 
         drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= line_duration))+
  geom_bar(color = "slateblue") +
  theme_minimal(base_size = 14)+
  ggforce::facet_zoom(xlim = c(0, 200), zoom.size = 1)

@@

# therapy_line %>% 
#   mutate(change_line = case_when(
#     linenumber == 1 & 
#       linenumber_new == 2 &
#       chemotherapy_type == "Adjuvant" &
#       treatment_sequence == "neo + surg + adj"     ~ 1,
#     TRUE                                           ~ 0
#   )) %>% 
#   filter(change_line == 1) %>% 
#   group_by(patientid) %>% 
#   mutate(firstdate = first(episodedate)) %>% 
#   mutate(lastdate = last(episodedate)) %>% 
#   ungroup() %>% 
#   mutate(time_of_switch_line = interval(start = firstdate, end = lastdate) / duration(n =1, units = "days")) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x=time_of_switch_line, fill = ..count..))+
#   geom_histogram(binwidth = 7)+
#   theme_minimal(base_size = 14)+
#   ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
#   scale_y_continuous(#breaks=c(0, 50, 100, 150),
#                      minor_breaks=c(10, 20, 30, 40)#,
#                      #labels = c(0, 50, 100, 150)
#   )
```
<!-- `r emo::ji("question_mark")`   -->
<!-- <span style="color:red">**So the bigger question is : Is it acceptable to include the patients who have a switched line?**</span> -->

@@

```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_creat = case_when(
    abs(interval_creat) < 31 &
      creat_date > linestartdate &
      creat_date < lineenddate             ~ interval_creat,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with weight
  left_join(. , weight, by = "patientid") %>%
  mutate(interval_weight = abs(interval(start= weight_date, end= cycle_start_date)/
                        duration(n=1, unit="days"))) %>%
  mutate(interval_weight = case_when(
    abs(interval_weight) < 31 &
      weight_date > linestartdate &
      weight_date < lineenddate             ~ interval_weight,
    TRUE                                    ~ NA_real_
  )) %>% 
  arrange(interval_weight) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
         cycle_start_date, .keep_all = TRUE) %>%

@@

  # Merge with body_surface_area
  left_join(., body_surface_area, by = "patientid") %>%
  mutate(interval_bsa = abs(interval(start= bsa_date, end= cycle_start_date)/
                          duration(n=1, unit="days"))) %>%
  mutate(interval_bsa = case_when(
    abs(interval_bsa) < 31 &
      bsa_date > linestartdate &
      bsa_date < lineenddate               ~ interval_bsa,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_bsa) %>%
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment,
           cycle_start_date, .keep_all = TRUE) %>%
  # Calculate more bsa value with height and weight using Du Bois formula
  mutate(bsa_du_bois = 0.007184 * ((height*100)^0.725) * (weight^0.425)) %>% # get pretty close results 4269 patients result
  mutate(BSA = coalesce(BSA, bsa_du_bois)) %>%
  mutate(bsa_du_bois = 0.007184 * ((height_at_dx*100)^0.725) * (weight_at_dx^0.425)) %>% # get pretty close results 4269 patients result
  mutate(bsa_at_dx = coalesce(bsa_at_dx, bsa_du_bois)) %>%
  select(-bsa_du_bois) %>%

  # Merge with auc
  left_join(., areaUC, by = c("patientid", "drugname")) %>%
  mutate(interval_auc = abs(interval(start= auc_date, end= cycle_start_date)/ # use episode date to be more precise? No it's not better
                          duration(n=1, unit="days"))) %>% 
  mutate(interval_auc = case_when(
    abs(interval_auc) < 31 &
      auc_date > linestartdate &
      auc_date < lineenddate               ~ interval_auc,
    TRUE                                   ~ NA_real_
  )) %>% 
  arrange(interval_auc) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

# II.Data analysis
## Explore the dataset

@@

### Number of line in treatment and cycle in frontline (more cleaning needs to be done here)
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Don't forget we have that "neo + surg"
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
<br>

@@

<span style="color:green">**Table 1 Overall summary demographic/clinical data**</span>
```{r Table 1}
analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(vital, raceeth, 
           agecat, "ageatdx",

@@

```{r Table 3}
# tbl1 <- 
  analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "debulking",
           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl2 <- analysis_data %>% distinct(patientid, .keep_all = TRUE) %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

@@

  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("highly underdose", "underdose", "correct", "perfect", "higher dose", "overdose")))

Frontline <- Frontline %>% 
  filter(str_detect(drugname, "platin|taxel"))
```

@@

## 2.Plots Clinical
<div class = "row">
<div class = "col-md-6">
```{r plot clinical}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "BMI category")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= histology))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Histology")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= stagecat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Stage")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= agecat))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Age cat")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_germline))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "BRCA gernline")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_tumor))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "BRCA tumor")+
  coord_flip()
```
</div>

<div class = "col-md-6">
```{r}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = bmi_cat))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "BMI category")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = histology))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Histology")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = stagecat))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Stage")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = agecat))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "Age cat")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = brca_germline))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "BRCA germline")+
  coord_flip()

Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = brca_tumor))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 14)+
  labs(title = "BRCA tumor")+
  coord_flip()
```
</div>
</div>

@@

```{r treatment table}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "resdz", "debulking", "diff_surg_dx",
           # had_neo, had_adj,
           "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p(
    # test.args = all_tests("chisq.test") ~ list(workspace=2e9)
    ) %>% bold_p(t = .05)
# tbl2 <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

## 2.Plots Treatment
<div class = "row">
<div class = "col-md-6">
```{r treatment plots}
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= issurgery))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Surgery")+
  coord_flip()

Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal(base_size = 14)+
  labs(title = "Frontline treatment")+
  coord_flip()

# Frontline %>% 
#   arrange(episodedate) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   group_by(chemotherapy_type) %>% 
#   summarize(count = n()) %>% mutate(percent=(count/sum(count)*100)) %>%
#   ggplot(aes(x= chemotherapy_type, y= percent, fill = chemotherapy_type))+
#   geom_bar(stat="identity")+
#   labs(x = "", title = "The first chemotherapy received by a patient Adjuvant for ~70% of the time") +
#   theme_minimal(base_size = 14)+
#   guides(fill = FALSE) +
#   coord_flip()
